### 2015-05-18 Manuscript/Missing_mammals-draft.tex
Changed to one sentence lines

\section{Introduction}
%We need fossils - dangerously paraphrased from the missing data paper
Studying both living and fossil taxa together in essential to fully understand macrovelutionary patterns and processes and is becoming increasingly common among evolutionary biologists \citep{jacksonwhat2006,quentaldiversity2010,dietlconservation2011,slaterunifying2013,fritzdiversity2013,Wood01032013}. Combining the global biodiversity by including both living and fossil in such studies allows, for example, to improve accuracy of the timing of diversification events \citep[e.g.][]{ronquista2012}, to better understand relationships among lineages \citep[e.g.][]{beckancient2014} or to infer biogeographical patterns through time \citep[e.g.][]{Meseguer01032015}. %And add STD paper? Or that's too much self cites?
%We can use TEM for that
In order to perform such analysis, one must efficiently combine living and fossil taxa data in macroevolutionary models. One trending method, called the Total Evidence method \citep{eernissetaxonomic1993,ronquista2012}, allows to combine molecular data from living taxa and morphological data from both living and fossil taxa in a supermatrix \citep[e.g.][]{pyrondivergence2011,ronquista2012,schragocombining2013,slaterunifying2013,beckancient2014,Meseguer01032015}. This method not only allows to use all the available data but also allows to treat fossil taxa as tips rather than nodes \textit{via} integrative phylogenetic inference methods such as tip-dating \citep{ronquista2012,Drummond01082012,Wood01032013,BEASTmaster}.

%But missing data in living taxa problem
However, the Total Evidence method requires, by definition, a lot of data. One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills \citep[e.g.][]{meredithimpacts2011} \textit{vs.} \citep{O'Leary08022013}. Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis. For example, fossil have really rarely molecular data available and morphological characters are rarely collected for living taxa when molecular data is available \citep[e.g.][]{slaterphylogenetic2013,beckancient2014}. This difference between both data can lead to topological errors in phylogenetic inference \citep{GuillermeCooper}. In fact, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between morphological data from the living and the fossil taxa \citep{GuillermeCooper}. The effect of missing data is most important on topology when too few living taxa have available morphological data \citep{GuillermeCooper}. For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data). This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \citep{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}.

>>>>

\section{Introduction}
Studying both living and fossil taxa together in essential to fully understand macrovelutionary patterns and processes and is becoming increasingly common among evolutionary biologists \citep{jacksonwhat2006,quentaldiversity2010,dietlconservation2011,slaterunifying2013,fritzdiversity2013,Wood01032013}.
Combining the global biodiversity by including both living and fossil in such studies allows, for example, to improve accuracy of the timing of diversification events \citep[e.g.][]{ronquista2012}, to better understand relationships among lineages \citep[e.g.][]{beckancient2014} or to infer biogeographical patterns through time \citep[e.g.][]{Meseguer01032015}.
%And add STD paper? Or that's too much self cites?
In order to perform such analysis, one must efficiently combine living and fossil taxa data in macroevolutionary models.
One trending method, called the Total Evidence method \citep{eernissetaxonomic1993,ronquista2012}, allows to combine molecular data from living taxa and morphological data from both living and fossil taxa in a supermatrix \citep[e.g.][]{pyrondivergence2011,ronquista2012,schragocombining2013,slaterunifying2013,beckancient2014,Meseguer01032015}.
This method not only allows to use all the available data but also allows to treat fossil taxa as tips rather than nodes \textit{via} integrative phylogenetic inference methods such as tip-dating \citep{ronquista2012,Drummond01082012,Wood01032013,BEASTmaster}.

However, the Total Evidence method requires, by definition, a lot of data.
One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills \citep[e.g.][]{meredithimpacts2011} \textit{vs.} \citep{O'Leary08022013}.
Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis.
For example, fossil have really rarely molecular data available and morphological characters are rarely collected for living taxa when molecular data is available \citep[e.g.][]{slaterphylogenetic2013,beckancient2014}.
This difference between both data can lead to topological errors in phylogenetic inference \citep{GuillermeCooper}.
In fact, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between morphological data from the living and the fossil taxa \citep{GuillermeCooper}.
The effect of missing data is most important on topology when too few living taxa have available morphological data \citep{GuillermeCooper}.
For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data).
This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \citep{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}.
